\section{Motivating Examples}
\label{sec:examples}

We first illustrate how \ourTool works and the nature of repair with the usage of
familiar API calls from the Java standard library, reflecting along the way on the differences between our and other tools for code completion and repair. To emphasize the significance in practical software development, 
our examples are chosen from a set of the real code examples (most of them featured at
\url{http://www.java2s.com/}{}).

\subsection{\ourTool as a Synthesis Tool}

Figure~\ref{fig:screenshot1} is a screen capture showing that \ourTool is also
a synthesis tool. In the scenario in Fig.~\ref{fig:screenshot1} the user already wrote some parts of the code, and now she 
needs to write a matcher. After declaring a variable,
she invokes \ourTool, which suggests a list of well-typed expressions that would fit here. Hopefully, the desired code is also among the returned results. It is the case in this particular example, and the user selects the third 
result, which is then automatically inserted in the program. The number of the results returned by \ourTool can be easily adjusted in the settings of the tool. 

Finding useful code snippets is an important aspect of every synthesis tool: it is not enough that 
the synthesized code can compile -- in addition it should also be the code that the user had in mind. It is not always possible to guess correctly the user's intentions, but as we show in Section~\ref{sec:evaluation}, \ourTool is able to suggest a desired code fragment in \ruzica{??} of benchmarks.

In Section~\ref{sec:algorithm} we explain in details how to generate ``most desired'' results. The \ourTool algorithm relies on a system of costs to accurately guess 
programmers' intentions. The system of costs is similar to the system of weights used 
in \cite{GveroETAL13CompleteCompletionTypesWeights}.

This smart auto-completion functionality is present in many tools \cite{MandelinetALL2005Jungloid, GveroETAL13CompleteCompletionTypesWeights, PerelmanGBG12}. 
The novelty present in \ourTool is auto-correction, and that we illustrate in following examples.


%After the initial JVM warm-up?  
%
%The following series of examples will demonstrate how to apply \ourTool in practical software
%development. These examples are written in the Java programming
%language. As formally defined in Sec.~\ref{sec:preliminaries},
%as input our algorithm takes terms in applicative long normal
%form, which closely corresponds to expressivity of the Java programming language.
%To emphasize the significance in practical software development, 
%we choose examples from a set of the real code examples (most of them featured at
%\url{http://www.java2s.com/}{}).
%
%
%
%We first illustrate our approach and the nature of repair with the usage of
%familiar API calls from the Java standard library, reflecting along the way on the differences
%between our and other approaches for code completion and repair.
%We then present somewhat more complex examples which illustrate the reach and
%the expressiveness in terms of possible expressions accepted as
%inputs and produced as outputs when using our automated code repair.
%In order


\subsection{Code Correction: Sequence of Streams}

We next show a difference between \ourTool and InSynth 
\cite{GveroETAL13CompleteCompletionTypesWeights}. We take an example
that is similar to the example presented in the InSynth paper to illustrate
how \ourTool handles a backbone 
expression that does not compile. 

Consider the following program fragment:
\begin{lstlisting}
import java.io.*;

public class Main {
  public static void main(String args[]) 
  throws IOException {
    String body = "email.txt";
    String sig = "sign.txt";
    
    SequenceInputStream seqStream = 
      new SequenceInputStream(body, sig) // error
  }
} 
\end{lstlisting}
The developer declared the variable \lstinline{seqStream}; however, the specified 
expression assigned to \lstinline{seqStream} does not compile. Still, from this backbone expression 
we can recognize the structure of the intended expression: our tool should construct 
an expression that preserves the relative position of the declarations from 
\lstinline{SequenceInputStream(body, sig)}. In the resulting expression a \lstinline{SequenceInputStream} constructor
should be used, with arguments that contain \lstinline{body} and \lstinline{sig} variables in their
corresponding sub-expression trees. \ourTool finds all such expressions, 
constructed from the
declarations visible in the scope of the backbone expression. The found expressions are well-typed 
and ranked according to a metric that characterizes the
resemblance to the starting backbone expression.
The returned expression with the highest rank is
\begin{lstlisting}
SequenceInputStream seqStream = 
new SequenceInputStream(
  new FileInputStream(body), new FileInputStream(sig))
\end{lstlisting}
This expression represents exactly the desired expression. This expression was found 
in \ruzica{??} milliseconds.
 
When we ran InSynth on the same example, but without the backbone expression, the desired expression was
ranked as the second highest. Our tool outperformed InSynth on this example, showing that the backbone expression can increase quality of the returned results.

An additional advantage that our repair algorithm has over InSynth is handling of constants. 
As an illustration, given the backbone expression:
\begin{lstlisting}
SequenceInputStream seqStream = 
   new SequenceInputStream("email.txt", "sign.txt") 
\end{lstlisting}
\ourTool returns, as expected:
\begin{lstlisting}
SequenceInputStream seqStream = 
  new SequenceInputStream(
    new FileInputStream("email.txt"), 
    new FileInputStream("sign.txt"))
\end{lstlisting}
Using InSynth we were not able to synthesize code snippets with arbitrary literals. 
This way our code repair algorithm can be considered as an improved synthesis algorithm,
because it also incorporates explicitly given literals in the final snippets.

%
%In this example, the developer's hint in terms of the broken expression
%unambiguously determines the result - it drives the repair process to
%produce the desired expression as the repaired expression with the highest rank.
%This shows that with giving the developer the possibility to specify
%the intent with additional constraints in terms of an expression that
%resembles the desired one, our approach can be very effective in driving the
%repair and finding the expression the developer had in mind.

\subsection{Use of Coercion Functions}

To address the problems that can arise with subtyping, we introduce 
coercion functions \cite{TannenCoercionS91}. 
They are used for type conversion and can be applied automatically if needed, 
without the direct intervention from the developer. For every subtyping relation $A<:B$, we introduce a coercion function $c$, s.t. $c: A \rightarrow B$. 
An automated insertion of
coercion functions is utilized for the purpose of fixing ill-typed
expressions in many modern compilers, but usually in a limited manner 
(at most one coercion function can be used to fix an ill-typed expression).
Our repair algorithm goes beyond this standard and allows more expressive 
transformations of ill-typed expressions. 

Consider the following code, in which the developer declares a byte buffer and
wants to construct an expression of the type \lstinline{InputStream} by merely hinting
the desired type and usage of the declared buffer \lstinline{b}:
\begin{lstlisting}
import java.io.*;

public class Main {
  public static void main(String args[]) 
  throws IOException {
    int off = 8, len = 512, size = 1024;
    byte b[] = args[0].getBytes();
    
    InputStream input = b; // error
  }
}
\end{lstlisting}

To repair the expression that initialize the variable \lstinline{input}, 
\ourTool inserts a coercion function (here represented as a constructor application):
\begin{lstlisting}    
InputStream input = new ByteArrayInputStream(b);
\end{lstlisting}
\ourTool returns this expression as the highest ranked expression: 
the expression is well-typed, follows the simple structure of the backbone
expression \lstinline{b}, with the smallest size. The value was computed in \ruzica{??} 
milliseconds. 
The upcasting done in this case can be seen as an implicit insertion of 
a coercion function, which casts \lstinline{ByteArrayInputStream} to
its superclass, \lstinline{InputStream}.

\ourTool returns additional well-typed expressions, such as 
\begin{lstlisting}    
InputStream input = 
   new ByteArrayInputStream(b, off, len);
\end{lstlisting}
This expression also correctly
repairs the given backbone expression, but it no longer represents a simple coercion
function insertion. It is the \lstinline{ByteArrayInputStream} overloaded 
constructor with three arguments. To create this expression, our algorithm
considers a broader range of available functions and finds appropriate
expressions that fill the places of the missing arguments. Those arguments
are synthesized whenever a type-conversion function requires additional parameters.

In general, the \ourTool algorithm is based on advanced methods for searching and adapting 
appropriate functions, combined with synthesizing any additional necessary
arguments.


%The functions visible at the program point where the algorithm is invoked.
% The algorithm can use all functions in the scope to repair the ill-typed expression.
% Here is another candidate expression our algorithm generates, more complex and longer, but valid
% result of the repair algorithm:
% \begin{lstlisting}    
% InputStream input = new SequenceInputStream(
%   new ByteArrayInputStream(b, off, len), new BufferedInputStream(System.in, size));
% \end{lstlisting}
%We can see that our approach can use all visible declarations to construct expressions of
%arbitrary complexity in place of \textit{boarding arguments} if necessary.
%The only restriction of such repair is that the resulting expression must follow
%the structure of the given broken expression in a certain manner (as an example, in this
%expression, the second argument to the \lstinline{SequenceInputStream} constructor may not
%contain \lstinline{b} in its expression).

\subsection{Mutations of Ill-typed Expressions}

%We next illustrate that our approach also considers modifications to the
%given ill-typed expression itself, i.e. mutations of it, during the search for
%the best fitting repair expression.

%The next example extensively uses calls to the
%standard Java API library for manipulation of streams.
Sometimes the developer writes an ill-typed code that less reflects
the structure of the desired expression. This is usually caused by giving a wrong order
or a number of arguments. 

Consider the following code that extensively uses
calls to the standard Java API library to manipulate streams.
The given backbone expression hints the user's intention to read a file 
compressed with the ZLIB library through a buffered stream.
To read the file, a user needs an \lstinline{InputStream} object.
\begin{lstlisting}
import java.io.*;
import java.util.zip.*;

public class Main {
  public static void main(String args[]) 
  throws IOException {
    int buffSize = 1024, compLevel = Deflater.BEST_SPEED;
    String fileName = "compressed.txt";
    
    InputStream input = 
      new BufferedInputStream(buffSize,
        new DeflaterInputStream(
           new FileInputStream, compLevel, true)); 
      // error
  }
}
\end{lstlisting}

In this example the user wrote arguments of 
the \lstinline{BufferedInputStream} constructor in a wrong order.

To correct this error and create a desired expression, 
\ourTool algorithm has to change the order of
the \lstinline{BufferedInputStream} arguments in the initial backbone expression.
After applying a set of further modifications to the arguments, we derive 
a new backbone expression: 
\lstinline{DeflaterInputStream(new FileInputStream, compLevel, true)}.
We recursively continue this procedure until we reach leaves in the
\ourTool graph (cf. Sec.~\ref{sec:algorithm}). Finally, the algorithm corrects the backbone expression
by inserting \lstinline{Deflater} constructor. At the end, \ourTool suggest the following correction for the above expression:
\begin{lstlisting}    
InputStream input = new BufferedInputStream(new DeflaterInputStream(
  new FileInputStream(fileName), new Deflater(compLevel, true)), buffSize);
\end{lstlisting}
\ourTool derive this code snippet in \ruzica{??} milliseconds. 

These examples have shown that our algorithm can perform a search through a large number of
possible repair expressions, and guides the procedure according to an appropriate metric
that characterizes the distance from the given broken expression.

We hope that \ourTool can indeed perform useful
and effective repairs that are well aligned with the developer's intent, even when
 the given ill-typed expression requires several steps of the repair.  




%Each mutation of an initial backbone expression introduces additional penalty 
%in terms of the resulting rank.
% mozda treba pomenuti da algoritam moze naci i gluplji expression sa mozda
% vecim rankom -> ne treba, prevelika je vec sekcija, i ovo cu baciti
% jer nemamo experimental evaluation.
%The algorithm is based on advanced methods for searching and adapting 
%appropriate functions, combined with synthesizing any additional necessary
%arguments.

