\section{Related Work}
\label{sec:related}

Our work is largly inspired by two synthesis tools: Prospector \cite{MandelinetALL2005Jungloid} and InSynth \cite{GveroETAL13CompleteCompletionTypesWeights, DBLP:conf/cav/GveroKP11}.
Prospector a a tool for synthesizing code snippets containing only API methods. The basic synthesis algorithm used in  a graph encoding of method signatures. As explained in Sec.~\ref{sec:algorithm:graph}
our synthesis graph is more general: in nodes we do not store only types, but also descriptions how a value of that type can be constructed. In a way, our node stores succint types introduced in  \cite{GveroETAL13CompleteCompletionTypesWeights}




Debugging and locating errors in the code \cite{Pavlinovic:2014,
  Chandra:2011:AD} play an important role in the process of increasing
software reliability. Once located, some errors can be easily
fixed. Recently we have witnessed to a number of tools that aim to
repair parts of code. MintHint \cite{MintHint} is such a tool that
takes a more complete-program approach to code repair. Where we are
using user input to guide synthesis of a correctly-typed expression
from an incorrectly-typed one, MintHint targets a particular passage
that is suspected to carry a bug. MintHint synthesizes some hints in
areas that the algorithm considers erroneous, by both symbolically and
actually executing the code and comparing its output to test cases.




gnatures are represented as explained earlier, in a directed
graph where the nodes are types and edges are expressions de-
rived from signatures. E


a graph algorithm for synthesizing expressions of a certain type. 

